%!TEX program = xelatex
\documentclass[UTF8]{article}
\usepackage{graphicx}
\usepackage{setspace}
% \usepackage{ctex}
\usepackage{indentfirst}
\setlength{\parindent}{2em}  % 用于首行缩进

\usepackage{amsmath}
\usepackage{amsthm} % 使用定理环境
\usepackage{amssymb}

\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,CJKbookmarks=True]{hyperref}  % 使用链接 但不用默认属性
% CJKbookmarks让链接支持中文
% \usepackage{hyperref}
% \usepackage{geometry}
% \geometry{a4paper,scale=0.8}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{geometry}
\geometry{a4paper,left=2.0cm,right=2.0cm,top=3.0cm,bottom=3.0cm}
\setstretch{1.5}   %  改变行间距
% \newgeometry{left = 2 cm, top= 3 cm}

\title{Summary}
\author{Dis\cdot count}
% \date{Feb 2019}

% \newtheorem{algorithm}{Algorithm}
\newtheorem{thm}{\hspace{2em}Theorem}
\newtheorem{lem}{\hspace{2em}Lemma}
\newtheorem{pf}{\hspace{2em}Proof}
\newtheorem{remark}{\hspace{2em}Remark}
%  \newtheorem{def}{Definition}  doesnt work

\begin{document}

\maketitle{}

\input{Chapters/Introduction}

\input{Chapters/Ch2}

%\input{Chapters/Outline}
\input{Chapters/Ch3}

\input{Chapters/Ch4}

\input{Chapters/Ch5}

\input{Chapters/Ch6}

Now we know the separation problem can be solved in $O(v^2)$ time and the breakpoints during the whole interval are polynomial, so for the IVPU game the PSPF function can be constructed in polynomial time.

\begin{thm}\label{thm6}
The IVPU game can be solved in polynomial time.
\end{thm}

Until here, we've solved the IVPU game with alternative machines.

Then, we will try to extend the core concept to a more general case. So we need to define a new game as follow.

\section*{Definition 2}

A cooperative TU game $(V,c)$ is a PIM(Price Integer Minimization) game if there exist:

\begin{itemize}
	\item positive integers e, v, t, P and m;
	\item integer vectors $ x \in \mathbb{Z}^{t \times 1} $and $ \tilde{\alpha} \in \mathbb{Z}^{1 \times t} $;
	\item left hand side matrix  $A \in \mathbb{R} ^{e \times t};$
	\item right hand side matrix $B \in \mathbb{R} ^ {e \times v};$
	\item a right hand side vector $D \in \mathbb{Z} ^ {e};$
	\item an objective function vector
	$c \in \mathbb{Z}^{1 \times t};$
	\item an incidence vector $y^s \in \{0,1\}^v$ with $y^s_k = 1$ if $k \in s$ and $y^s_k = 0 $ otherwise, $\forall k \in V$,

\end{itemize}

such that the characteristic function $c(s)$ equals the optimal objective value of the following integer linear program:

\[
c(s,P)= \mathop{\min}_{x} \{ cx+Pm(x): Ax \geq By^s+D, \tilde{\alpha}x \leq m, x \in \mathbb{Z}^{t \times 1} \}
\]

Note that the object function is not easy to analyze due to the joint effct of $cx$ and $Pm$, we need to divide the function into two parts for a further discussion.

With this idea, we divide $c(s,m(s,P))$ as $c_0(s,m(s))+Pm $. Via analysis and study, we find some properties about $c_0(s,m(s)) $ which we call primary function later.

The primary function must be supermodular, then we can get the positive price or setup cost when the number of facilities changes. This corresponds to the following two lemmas.


\begin{lem}\label{lem2}
% \\ \hspace*{\fill} \\ % 用于空行
% ~\\
\[c_0(V,m)- c_0(V,m-1) > 0 \Leftrightarrow P_m > 0, m=2,\ldots,n.\]

\end{lem}

\begin{lem}\label{lem3}
\[
\begin{aligned}
&c_0 (V,m) - c_0 (V,m+1) < c_0 (V,m-1) - c_0 (V,m) \\
&\Leftrightarrow \quad P_m < P_{m+1} , m=2,3,\ldots,n.
\end{aligned}
\]
\end{lem}

Once the primary function must be supermodular, we can specify this property in the following two aspects.
One is the concavity about the number of facilities,
the other is the nature about the number of players($s_1 \subset s_2$).
They correspond to the following two formulas:

\begin{equation}\label{concavity_f}
c_0(s_1,m-1)-c_0(s_1,m) \geq
  c_0(s_1,m)-c_0(s_1,m+1) \quad m=2,\ldots,n.
\end{equation}
% 只要这里是关于机器数量的变化即可
and

\begin{equation}\label{property_p}
	c_0(s_1,m-1)-c_0(s_1,m) \leq
	  c_0(s_2,m-1)-c_0(s_2,m) \quad m=2,\ldots,n.
\end{equation}
, respectively.
% 只要这里是关于players的变化即可

If the characteristic function satisfies the above property. Then $ P_1$ can be calculated by the following procedure:
When $\alpha(V) = c_0(V) + P_1$, which means the $\omega(P_1) = 0$. And the active inequalities must be the coalition contains $(n-1)$ players.
Then plus all the $(n+1)$ equality together, we can obtain $P_1 = (n-1)c(V)- \sum_{|s|=n-1,s\in S}c(s)$.
Because other inequalities will be satisfied according to the supermodular.

Then we can develop the Theorem \ref{thm7}.

\begin{thm}\label{thm7}
When two coalitions $s_1,s_2$ satisfy $s_1 \subset s_2$, the corresponding number of using facilities $ m_{s_1}, m_{s_2}$ have $m_{s_1} \leq m_{s_2}$, if the primary function satisfies  (\ref{concavity_f}) and (\ref{property_p}).
\end{thm}

\begin{lem}\label{lem4}
When $c_0(s)$ satisfy the supermodular and $P=P_1$, where $m_V=1$, if $\alpha(s)=c(s)+P_1, \left| s \right|= n-1$ and $\alpha(V)=c_0(V)+P_1$ the budget balance constraint holds, the other coalitional stability constraints $\alpha(s) \leq c(s)+P_1, \left| s \right| < n-1$ will hold.
\end{lem}

\input{Chapters/Proof}

The IPU game is very special so that we can use SPT rule to compute the $c_{IPU}(s)$ , which means jobs in coalition $s$ with the shortest processing time should be processed first and the longest ones last. Then we can use dynamic programming to solve the separation problem $\delta_{IPU} = \min \big\{c_{IPU}(s)+P-\bar{\alpha}(s,P): \forall s \in \mathbb{S} \setminus \{N\}\big\} $


\end{document}
